### 2021-03-05 ch/1-introduction.tex
Incorporate Novi's feedback for chapter 1

When evaluating models in these setup,
the problem is often that we do not have access to the underlying true unbiased dataset.
In this case, we cannot just rely on metrics like accuracy to compare models:
the model is not being evaluated on the right dataset, so accuracy is not that informative.
For these cases, where we do not have access to a truly unbiased test set,
we use \emph{fairness metrics}, which do not rely on access to an unbiased set.
These fairness metrics, which are based on different fairness definitions,
are then used alongside metrics like accuracy to evaluate how well a model has corrected for the training set bias.
Note however, that evaluation on a truly unbiased dataset is still preferred:
fairness metrics make assumptions about what it means to be unbiased that might not fit the actual use case.

While fairness metrics are primarily useful when no truly unbiased test sets are provided,
even when they are provided,
these metrics can be useful in identifying where models retained some of the bias from the training set.

The fairness definition that best fits the described setup of label bias and sampling bias is \acf{DP},
also called statistical parity or independence.
It demands that the predictions $\hat{y}$ be independent of the sensitive attribute \(s\).
So, for binary $s$ and $y$:
\begin{align}
  P(\hat{y}=1|s=0) &= P(\hat{y}=1|s=1)~.
  \label{eq:dp-def}
\end{align}
There are multiple \ac{DP} \emph{metrics} which track how close the predictions are to satisfying the equality,
among them the difference and the ratio of the terms on the two sides of the equation.

>>>>

The overall goal in all cases is to make the classifier invariant to $s$.
We can measure the invariance to $s$ directly by using \emph{fairness metrics}
on the predictions of the classifier.
In contrast to the accuracy metric,
these fairness metrics give a more complete picture of how invariant the classifier is.
This is especially true if evaluation is done on an imbalanced set
-- for example because a truly unbiased test set is not available.
In this case, accuracy can be highly misleading,
because a good performance in the majority class can hide a poor performance in a minority class.
Fairness metrics do not suffer from this problem,
because they specifically look at the results in the different subgroups.
However, we typically try to evaluate our models on a test set that is as unbiased as possible,
in order to have a meaningful accuracy.

The fairness definition with the clearest interpretation in the described setup of label bias and sampling bias is \acf{DP},
also called statistical parity or independence.
It demands that the predictions $\hat{y}$ be independent of the sensitive attribute \(s\).
So, for binary $s$ and $y$:
\begin{align}
  P(\hat{y}=1|s=0) &= P(\hat{y}=1|s=1)~.
  \label{eq:dp-def}
\end{align}
There are multiple \ac{DP} \emph{metrics} which track how close the predictions are to satisfying the equality,
among them the difference and the ratio of the terms on the two sides of the equation.
